\thesistitle

### 2019-08-24 sections/conclusion.tex

>>>>

\subsection{Aggregated Maintainability Score}
In Section~\ref{sec:metricformula} we proposed an aggregation to measure a maintainability score on small grained changes. The assumptions stated in this section influence the validity of the maintainability scores shown in our results. We noticed that the maintainability scores shown in Table~\ref{tab:relationref} and Table~\ref{tab:return} were mostly influenced by the differences in the ``number of parameters'' metric. This is because for the scores, we normalized the metrics over all values obtained by these metrics. As our data regarding ``number of parameters'' has a very low standard deviation, small changes in this metric will influence the maintainability score a lot.
